### 2018-11-09 Sabanci_talk/Sabanci_talk.tex
More slides more figures

%\documentclass[xcolor=dvipsnames,t]{beamer}
\documentclass[xcolor=dvipsnames,handout,t]{beamer}
% use handout in document class to stop transitions

@@

\newcommand{\Mag}{\textcolor{magenta}}
\newcommand{\Red}{\textcolor{red}}
\newcommand{\Blue}{\textcolor{blue}}
\renewcommand{\c}{\cos}
\renewcommand{\t}{\theta}
\renewcommand{\b}{\bar}
\newcommand{\f}{\frac}
\newcommand{\bt}{\beta}
%\newcommand{\s}{\sin}
\newcommand{\ph}{\phi}
\newcommand{\g}{\gamma}
\newcommand{\nn}{\nonumber}
\newcommand{\la}{\lambda}
\newcommand{\al}{\alpha}
\newcommand{\La}{\Lambda}
\newcommand{\el}{\ell}
\newcommand{\h}{\hat}
\newcommand{\mrm}{\mathrm}
\newcommand{\ord}{\mathcal{O}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\ba}{\begin{eqnarray}}
\newcommand{\ea}{\end{eqnarray}}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\bef}{\begin{frame}}
\newcommand{\ef}{\end{frame}}
%\newcommand{\h}{\bar{h}}
\newcommand{\bs}{\begin{small}}
\newcommand{\es}{\end{small}}
\newcommand{\parallelsum}{\mathbin{\!/\mkern-5mu/\!}}
\newcommand{\Lim}[1]{\raisebox{0.5ex}{\scalebox{0.8}{$\displaystyle \lim_{#1}\;$}}}
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{\node[shape=circle,draw,inner sep=2pt] (char) {#1};}}
%------------------ for coloured boxes in math modes --------------------
% Syntax: \colorboxed[<color model>]{<color specification>}{<math formula>}
\newcommand*{\colorboxed}{}
\def\colorboxed#1#{%
  \colorboxedAux{#1}%
}
\newcommand*{\colorboxedAux}[3]{%
  % #1: optional argument for color model
  % #2: color specification
  % #3: formula
  \begingroup
    \colorlet{cb@saved}{.}%
    \color#1{#2}%
    \boxed{%
      \color{cb@saved}%
      #3%
    }%
  \endgroup
}
%%-------------------------------------------------------------------------

@@

\begin{frame}{Outline}
\begin{itemize}
 \item Motivation
 \item Gamma-ray bursts
 \item Gravitational waves
 \item Binary neutron star inspirals
 \item Gravitational-wave detectors
 \item Event rates 
\end{itemize}
\todo{finish this slide remove later if short on time}

@@

\begin{frame}{Motivation: Multi-messenger Astronomy}
  \begin{itemize}
    \item \emph{Multi}: two fundamentally different waves from common events.
    \item[]\quad Gravitational waves (GWs): ``hearing''  the universe.
    \item[]\quad Electromagnetic waves (EWs): ``seeing'' the universe.
    \item \red{GW170817}-\bl{GRB170817A}-\textcolor{brown}{AT2017gfo}: the ``event'' \\
    \quad inspiral + merger of two neutron stars (GWs) \\
    \ \ = short-hard gamma-ray burst + kilonova (EWs)
    \item[] Broad-band in gravitational waves: 10Hz - 2000Hz
    \item[] Ultra broad-band in electromagnetic waves: gamma rays to radio.
    \item A simple question \\
    {\small ``What can we offer to the astronomy community with future GW detections?''}
  \end{itemize}
\end{frame}

@@

 \begin{frame}{GW Detectors: \red{Interferometers}}
  Two geodesics separated by $\xi^\mu$:
  %\[
  % \frac{D^2 \xi^\alpha}{D\tau^2} = -R^\alpha_{\beta \gamma\delta}\, \xi^\gamma u^\beta u^\delta 
  %\]
$ \tfrac{d^2 \xi^i}{d\tau^2} = -R^i_{0j0} \xi^j\left(\tfrac{dx^0}{d\tau}\right)^2$ \hfill (detector frame)\\
%\hspace{4cm} $\Longrightarrow \ddot{\xi^i} = -c^2 R^i_{0j0} \xi^j $ \hfill (detector time)\ \\
\vspace{-3mm}
\[
\hspace{4.5cm} \boxed{\ddot{\xi^i} = \frac{1}{2} \ddot{h}_{ij}^\text{TT} \xi^j} \hspace{2.5cm} \text{(detector time)}
\]
%
%
GW along $\mathbf{z}$: 
\[
 h_{ij}^\text{TT} = \left(\begin{array}{cc}
                           h_+ & h_\times \\
                           h_\times & - h_+
                          \end{array}\right) \cos\left(\omega\left( t-\tfrac{z}{c}\right)\right)
\]
Consider mirrors at $(0,0)_1, (L,0)_2$ and $(L,L)_3$
\begin{small}
\begin{align*}
  s_{12} &= \int_1^2 \tfrac{ds}{dx}dx = (x_2-x_1) \left[ 1 + h_+ \cos(\omega t)\right]^{1/2}\hspace{4cm} \\
			      & \approx L \left[ 1+\tfrac{1}{2} h_+ \cos\omega t \right] \\
s_{13} &\approx L \left[ 1-\tfrac{1}{2} h_+ \cos\omega t \right]
\end{align*}
\end{small}
%
\begin{tikzpicture}[overlay,remember picture]
 \node[anchor=center,scale=1,opacity=1] at ([shift={(2cm,-3.4cm)}]current page.center){\todo{Make sure the vid here works}} ;
%\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(3.8cm,-2.8cm)}]current page.center) {\animategraphics[loop,controls,height=2.39cm]{12}{LIGO_int-}{0}{102}};
\end{tikzpicture}
 \end{frame}

\begin{frame}{Interferometers : \red{L}-topology}{LIGO, Virgo, KAGRA}
\vspace{-2mm}
  Interferometers ({\bf IFO}s) measure only the response function (\bl{GW strain})
  \begin{footnotesize}
  \begin{align*}
   h(t) &= F_+(\theta,\phi,\psi) \,h_+(t)+F_\times(\theta,\phi,\psi)\, h_\times(t) , \\
    F_+ &=\f{1}{2}\left(1+\cos^2\theta\right)\cos2\phi\cos 2\psi-\cos\theta \sin2\phi \sin2\psi, \\
    F_\times &=\f{1}{2}\left(1+\cos^2\theta\right)\cos2\phi\sin2\psi+\cos\theta \sin2\phi \cos2\psi
    \end{align*}
    \end{footnotesize}
   %
   Fourier transform to frequency domain 
  \begin{footnotesize}
  \begin{align*}
  &\red{\tilde{h}(f)} =A\, \underbrace{\f{c}{D}\left(\f{G M_c}{c^3}\right)^{5/6}}_{\bl{h_0}} \,\red{f^{-7/6}}\, e^{i\Psi}\, Q(\theta,\phi,\psi,\iota),\hspace{5cm} \\
     &\quad Q(\theta,\phi,\psi,\iota) = F_+\f{1+\cos^2\iota}{2}  + i F_\times \cos\iota \\
   &\quad A\equiv \pi^{-2/3}\sqrt{\tfrac{5}{24}}\\
   &\quad \Psi = \Psi_N(f) + \text{PN corrections}
    \end{align*}
    \end{footnotesize}
   \red{Four} angles: $\{\theta,\phi,\iota,\psi \}$
   %
  \begin{tikzpicture}[overlay,remember picture]
  \node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(3.8cm,-1.8cm)}]current page.center) {\includegraphics[height=5cm]{figs/Schutz_LRR_Fig3_half.jpg}};
  \end{tikzpicture}

@@

\begin{frame}{Interferometers : \red{Triangular}-topology}{Einstein Telescope}
\vspace{-2mm}
  Three $60^\circ$ V-IFOs, one redundant (null stream), $\sin 60^\circ =\sqrt{3}/2$.
  \begin{footnotesize}
  \begin{align*}
    &F^1_+(\theta,\phi,\psi)= \f{\sqrt{3}}{2} F_+(\theta,\phi,\psi), \qquad F^1_\times(\theta,\phi,\psi)= \f{\sqrt{3}}{2} F_\times(\theta,\phi,\psi),\hspace{2cm}\\
    & F^2_{+,\times}(\theta,\phi,\psi) = F^1_{+,\times}(\theta,\phi+2\pi/3,\psi)\qquad (\text{rotation by 120}^\circ),\\
    & F^3_{+,\times}(\theta,\phi,\psi) = F^1_{+,\times}(\theta,\phi-2\pi/3,\psi) \qquad(\text{rotation by 240}^\circ),\\
    &  |Q(\theta,\phi,\psi,\iota)|_\bigtriangleup^2 = \sum_{A=1}^3 \left(F^A_+\right)^2\f{1+\cos^2\iota}{2}  + \left(F^A_\times\right)^2 \cos\iota
    \end{align*}
    \end{footnotesize}
   %
   No blind spots!
   \begin{footnotesize}
  \begin{align*}
   F^2_\bigtriangleup &\equiv \sum_{A=1}^3 \left(F^A_+\right)^2+\left(F^A_\times\right)^2 \hspace{8cm}\\ 
   &= \f{9}{32}\left(1+6\cos^2\theta + \cos^4\theta\right)
  \end{align*}
  \end{footnotesize}
  %
  %
  \begin{tikzpicture}[overlay,remember picture]
  \node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(4.4cm,-1.cm)}]current page.center) {\includegraphics[height=3cm]{figs/gr_qc_12013563.png}};
   \node (img1 )[anchor=center,scale=1,opacity=1] at ([shift={(0.4cm,-2.5cm)}]current page.center) {\includegraphics[height=4cm]{../Figures/ET_no_blind_spots.pdf}};
    \node[anchor=center,scale=0.5,opacity=1] at ([shift={(5cm,0.4cm)}]current page.center) {Phys. Rev. D 86, 122001 };
  \end{tikzpicture}

@@

\begin{frame}{Detection criteria}{Optimal Signal-to-Noise Ratio ({\bf SNR})}
\vspace{-5mm}
\begin{footnotesize} 
\[
 \rho=\left[ \int_0^\infty d\ln f\, \f{|\red{2\tilde{h}(f)\sqrt{f}}|^2}{S_n(f)}\right]^{1/2} 
\]
\\
\end{footnotesize}
$\sqrt{S_n(f)}\equiv$ {\it amplitude spectral density} ({\bf ASD}) or  detector noise
\\
\vspace{3mm}
Recall, $\tilde{h}(f) \sqrt{f} \sim f^{-7/6} f^{1/2} = \red{f^{-2/3}}$
\begin{footnotesize} 
\[
 \rho^2 =  (2A)^2 h_0^2 |Q(\theta,\phi,\psi,\iota)|^2 \int_0^{\bl{f_\text{ISCO}}} df \f{f^{-7/3}}{S_n(f)} 
\]
\end{footnotesize}
%
RMS \red{average} over the angles 
\begin{small}
$ \langle \ldots \rangle \equiv \int \sin\theta d\theta d\phi \int d\psi \int\sin\iota d\iota $
\end{small}
\begin{footnotesize} 
\[
 \langle |Q(\theta,\phi,\psi,\iota)|^2 \rangle_\llcorner = \f{4}{25}, \qquad \langle |Q(\theta,\phi,\psi,\iota)|^2 \rangle_\triangle = \f{9}{25}
\]
\end{footnotesize}
%
Sources will have random $\{\theta,\phi,\psi,\iota\}$ \\
\begin{footnotesize} 
\[
0 \le Q(\theta,\phi,\psi,\iota) \le \underbrace{Q_\text{max}(\theta,\phi,\psi,\iota)}_{\theta=\tfrac{\pi}{2},\psi=0,\iota=0}
\]
\end{footnotesize}
% 
\end{frame}

>>>>

\documentclass[xcolor=dvipsnames,t]{beamer}
%\documentclass[xcolor=dvipsnames,handout,t]{beamer}
% use handout in document class to stop transitions

@@

\newcommand{\Mag}{\textcolor{magenta}}
\newcommand{\Red}{\textcolor{red}}
\newcommand{\Blue}{\textcolor{blue}}
\renewcommand{\c}{\cos}
\renewcommand{\t}{\theta}
\renewcommand{\b}{\bar}
\newcommand{\f}{\frac}
\newcommand{\bt}{\beta}
%\newcommand{\s}{\sin}
\newcommand{\ph}{\phi}
\newcommand{\g}{\gamma}
\newcommand{\nn}{\nonumber}
\newcommand{\la}{\lambda}
\newcommand{\al}{\alpha}
\newcommand{\La}{\Lambda}
\newcommand{\el}{\ell}
\newcommand{\h}{\hat}
\newcommand{\mrm}{\mathrm}
\newcommand{\ord}{\mathcal{O}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\ba}{\begin{eqnarray}}
\newcommand{\ea}{\end{eqnarray}}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\bef}{\begin{frame}}
\newcommand{\ef}{\end{frame}}
%\newcommand{\h}{\bar{h}}
\newcommand{\bs}{\begin{small}}
\newcommand{\es}{\end{small}}
\newcommand{\parallelsum}{\mathbin{\!/\mkern-5mu/\!}}
\newcommand{\Lim}[1]{\raisebox{0.5ex}{\scalebox{0.8}{$\displaystyle \lim_{#1}\;$}}}
\newcommand\T{\rule{0pt}{2.6ex}}       % Top strut for vertical spacing in tables
\newcommand\B{\rule[-1.2ex]{0pt}{0pt}} % Bottom strut
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{\node[shape=circle,draw,inner sep=2pt] (char) {#1};}}
%------------------ for coloured boxes in math modes --------------------
% Syntax: \colorboxed[<color model>]{<color specification>}{<math formula>}
\newcommand*{\colorboxed}{}
\def\colorboxed#1#{%
  \colorboxedAux{#1}%
}
\newcommand*{\colorboxedAux}[3]{%
  % #1: optional argument for color model
  % #2: color specification
  % #3: formula
  \begingroup
    \colorlet{cb@saved}{.}%
    \color#1{#2}%
    \boxed{%
      \color{cb@saved}%
      #3%
    }%
  \endgroup
}
%%-------------------------------------------------------------------------

@@

\begin{frame}{Outline}
\begin{itemize}
 \item Motivation
 \item Gamma-ray bursts
 \item Gravitational waves
 \item Binary neutron star inspirals
 \item Gravitational-wave detectors
 \item Future detectors, event rates, \red{early warning} prospects
\end{itemize}
\todo{finish this slide remove later if short on time}

@@

\begin{frame}{Motivation: Multi-messenger Astronomy}
  \begin{itemize}
    \item \emph{Multi}: two fundamentally different waves from common events.
    \item[]\quad Gravitational waves (GWs): ``hearing''  the universe.
    \item[]\quad Electromagnetic waves (EWs): ``seeing'' the universe.
    \item \red{GW170817}-\bl{GRB170817A}-\textcolor{brown}{AT2017gfo}: the ``event'' \\
    \quad inspiral + merger of two neutron stars (GWs) \\
    \ \ = short-hard gamma-ray burst + kilonova (EWs)
    \item[] Broad-band in gravitational waves: 10Hz - 2000Hz
    \item[] Ultra broad-band in electromagnetic waves: gamma rays to radio.
    \item A simple question \\
    {\small ``What can we offer to the astronomy community with future GW detections?''}
    Advance warning!
  \end{itemize}
\end{frame}

@@

 \begin{frame}{GW Detectors: \red{Interferometers}}
    Two geodesics separated by $\xi^\mu$:
    %\[
    % \frac{D^2 \xi^\alpha}{D\tau^2} = -R^\alpha_{\beta \gamma\delta}\, \xi^\gamma u^\beta u^\delta 
    %\]
    $ \tfrac{d^2 \xi^i}{d\tau^2} = -R^i_{0j0} \xi^j\left(\tfrac{dx^0}{d\tau}\right)^2$ \hfill (detector frame)\\
    %\hspace{4cm} $\Longrightarrow \ddot{\xi^i} = -c^2 R^i_{0j0} \xi^j $ \hfill (detector time)\ \\
    \vspace{-3mm}
    \[
    \hspace{4.5cm} \boxed{\ddot{\xi^i} = \frac{1}{2} \ddot{h}_{ij}^\text{TT} \xi^j} \hspace{2.5cm} \text{(detector time)}
    \]
    %
    %
    \onslide<2->
    {
      GW along $\mathbf{z}$: 
      \[
      h_{ij}^\text{TT} = \left(\begin{array}{cc}
				h_+ & h_\times \\
				h_\times & - h_+
				\end{array}\right) \cos\left(\omega\left( t-\tfrac{z}{c}\right)\right)
      \]
    }
    \onslide<3->
    {
      Consider mirrors at $(0,0)_1, (L,0)_2$ and $(L,L)_3$
      \begin{small}
      \begin{align*}
	s_{12} &= \int_1^2 \tfrac{ds}{dx}dx = (x_2-x_1) \left[ 1 + h_+ \cos(\omega t)\right]^{1/2}\hspace{4cm} \\
				    & \approx L \left[ 1+\tfrac{1}{2} h_+ \cos\omega t \right] \\
      s_{13} &\approx L \left[ 1-\tfrac{1}{2} h_+ \cos\omega t \right]
      \end{align*}
      \end{small}
    }
    %
    \onslide<4->
    {
      \begin{tikzpicture}[overlay,remember picture]
      \node[anchor=center,scale=1,opacity=1] at ([shift={(2cm,-3.4cm)}]current page.center){\todo{Make sure the vid here works}} ;
      %\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(3.8cm,-2.8cm)}]current page.center) {\animategraphics[loop,controls,height=2.39cm]{12}{LIGO_int-}{0}{30}};
      \end{tikzpicture}
    }
 \end{frame}

\begin{frame}{Interferometers : \red{L}-topology}{LIGO, Virgo, KAGRA}
  \vspace{-2mm}
  Interferometers ({\bf IFO}s) measure only the response function (\bl{GW strain})
  \begin{footnotesize}
  \begin{align*}
   h(t) &= F_+(\theta,\phi,\psi) \,h_+(t)+F_\times(\theta,\phi,\psi)\, h_\times(t) , \\
    F_+ &=\f{1}{2}\left(1+\cos^2\theta\right)\cos2\phi\cos 2\psi-\cos\theta \sin2\phi \sin2\psi, \\
    F_\times &=\f{1}{2}\left(1+\cos^2\theta\right)\cos2\phi\sin2\psi+\cos\theta \sin2\phi \cos2\psi
   \end{align*}
   \end{footnotesize}
   %
   \onslide<2->
   {
      Fourier transform to frequency domain 
      \begin{footnotesize}
      \begin{align*}
      &\red{\tilde{h}(f)} =A\, \underbrace{\f{c}{D}\left(\f{G M_c}{c^3}\right)^{5/6}}_{\bl{h_0}} \,\red{f^{-7/6}}\, e^{i\Psi}\, Q(\theta,\phi,\psi,\iota),\hspace{5cm} \\
	&\quad Q(\theta,\phi,\psi,\iota) = F_+\f{1+\cos^2\iota}{2}  + i F_\times \cos\iota \\
      &\quad A\equiv \pi^{-2/3}\sqrt{\tfrac{5}{24}}\\
      &\quad \Psi = \Psi_N(f) + \text{PN corrections}
	\end{align*}
	\end{footnotesize}
    }
    \onslide<3->
    {
      \red{Four} angles: $\{\theta,\phi,\iota,\psi \}$
      %
      \begin{tikzpicture}[overlay,remember picture]
      \node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(3.8cm,-1.8cm)}]current page.center) {\includegraphics[height=5cm]{figs/Schutz_LRR_Fig3_half.jpg}};
      \node[anchor=center,scale=0.5,opacity=1] at ([shift={(4.1cm,-4.4cm)}]current page.center){Sathyaprakash, Schutz, Living Rev. Relativ. (2009) 12:2} ;
      \end{tikzpicture}
    }   
\end{frame}

\begin{frame}{Interferometers : \red{Triangular}-topology}{Einstein Telescope}
  \vspace{-2mm}
  Three $60^\circ$ V-IFOs, one redundant (null stream), $\sin 60^\circ =\sqrt{3}/2$.
  \begin{footnotesize}
  \begin{align*}
    &F^1_+(\theta,\phi,\psi)= \f{\sqrt{3}}{2} F_+(\theta,\phi,\psi), \qquad F^1_\times(\theta,\phi,\psi)= \f{\sqrt{3}}{2} F_\times(\theta,\phi,\psi),\hspace{2cm}\\
    & F^2_{+,\times}(\theta,\phi,\psi) = F^1_{+,\times}(\theta,\phi+2\pi/3,\psi)\qquad (\text{rotation by 120}^\circ),\\
    & F^3_{+,\times}(\theta,\phi,\psi) = F^1_{+,\times}(\theta,\phi-2\pi/3,\psi) \qquad(\text{rotation by 240}^\circ),\\
    &  |Q(\theta,\phi,\psi,\iota)|_\bigtriangleup^2 = \sum_{A=1}^3 \left(F^A_+\right)^2\f{1+\cos^2\iota}{2}  + \left(F^A_\times\right)^2 \cos\iota
    \end{align*}
    \end{footnotesize}
   %
    \begin{tikzpicture}[overlay,remember picture]
    \node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(4.4cm,-1.cm)}]current page.center) {\includegraphics[height=3cm]{figs/gr_qc_12013563.png}};
    \node[anchor=center,scale=0.5,opacity=1] at ([shift={(5cm,0.4cm)}]current page.center) {Phys. Rev. D 86, 122001 };
    \end{tikzpicture}
    %
   \onslide<2->
   {
      No blind spots!
      \begin{footnotesize}
      \begin{align*}
      F^2_\bigtriangleup &\equiv \sum_{A=1}^3 \left(F^A_+\right)^2+\left(F^A_\times\right)^2 \hspace{8cm}\\ 
      &= \f{9}{32}\left(1+6\cos^2\theta + \cos^4\theta\right)
      \end{align*}
      \end{footnotesize}
  %
  %
  \begin{tikzpicture}[overlay,remember picture]

   \node (img1 )[anchor=center,scale=1,opacity=1] at ([shift={(0.4cm,-2.5cm)}]current page.center) {\includegraphics[height=4cm]{../Figures/ET_no_blind_spots.pdf}};
    \end{tikzpicture}
  }

@@

\begin{frame}{Detection criteria}{Optimal Signal-to-Noise Ratio ({\bf SNR})}
  \vspace{-5mm}
  \begin{footnotesize} 
  \[
  \rho=\left[ \int_0^\infty d\ln f\, \f{|\red{2\tilde{h}(f)\sqrt{f}}|^2}{S_n(f)}\right]^{1/2} 
  \]
  \\
  \end{footnotesize}
  $\sqrt{S_n(f)}\equiv$ {\it amplitude spectral density} ({\bf ASD}) or  detector noise
  \\
  \onslide<2->
  {
    \vspace{3mm}
    Recall, $\tilde{h}(f) \sqrt{f} \sim f^{-7/6} f^{1/2} = \red{f^{-2/3}}$
    \begin{footnotesize} 
    \[
    \rho^2 =  (2A)^2 h_0^2 |Q(\theta,\phi,\psi,\iota)|^2 \int_0^{\bl{f_\text{ISCO}}} df \f{f^{-7/3}}{S_n(f)} 
    \]
    \end{footnotesize}
  }
  %
  \onslide<3->
  RMS \red{average} over the angles 
  \begin{small}
  $ \langle \ldots \rangle \equiv \int \sin\theta d\theta d\phi \int d\psi \int\sin\iota d\iota $
  \end{small}
  \begin{footnotesize} 
  \[
  \langle |Q(\theta,\phi,\psi,\iota)|^2 \rangle_\llcorner = \f{4}{25}, \qquad \langle |Q(\theta,\phi,\psi,\iota)|^2 \rangle_\triangle = \f{9}{25}
  \]
  \end{footnotesize}
  %
  Sources will have random $\{\theta,\phi,\psi,\iota\}$ \\
  \begin{footnotesize} 
  \[
  0 \le Q(\theta,\phi,\psi,\iota) \le \underbrace{Q_\text{max}(\theta,\phi,\psi,\iota)}_{\theta=\tfrac{\pi}{2},\psi=0,\iota=0}
  \]
  \end{footnotesize}
  % 
\end{frame}

\begin{frame}{L-IFO vs. $\bigtriangleup$-IFO Networks}
\red{Three L}-IFOs, e.g., LIGO L1, H1 + Virgo
%
  \begin{footnotesize} 
  \begin{align*}
  \rho_{\text{tot},\llcorner} &= \left[{\sum_{i=1}^3 \rho^2_i}\right]^{1/2} =\left[ \rho_h^2 + \rho_m^2 + \rho^2_l \right]^{1/2} 
	  = {\rho_c\left[\tilde{A}_h^2 + \tilde{A}_m^2 + \tilde{A}_l^2 \right]^{1/2}}\\
  \rho_c &\equiv 2 h_0 \left[ \int_0^{{f_\text{ISCO}}} df \f{f^{-7/3}}{S_n(f)}  \right]^{1/2}, \quad \left\{ \tilde{A}_h = \tfrac{4}{5}A,  \tilde{A}_m =\tfrac{2}{5}A,  \tilde{A}_l  < \tfrac{\tilde{A}_m}{2}\right\}
  \end{align*}
  \end{footnotesize}
  %
  \begin{tikzpicture}[overlay,remember picture]
  \node[draw, red,thick,minimum width=3.5cm,minimum height=0.8cm] (b) at (8.8,1.9){};
  \end{tikzpicture}
  \\
  %\vspace{2mm}
  \onslide<2->
  {
    $\bigtriangleup$ = \red{Three V-}IFOs: Einstein Telescope
    \begin{footnotesize} 
    \[
    \rho^2_{\text{tot},\bigtriangleup} = \sum_{A=1}^3 \left(\rho^A\right)^2  =  A^2 \rho_c^2 \,|Q(\theta,\phi,\psi,\iota)|_\bigtriangleup^2 %\int_0^{f_\text{ISCO}} d f\, \f{f^{-7/3}}{S_n(f)} \,
    \]
    \end{footnotesize}
    \\
  }
  \onslide<3->
  Use \bl{RMS-averaged} $|Q|^2$
  \begin{footnotesize}
  \begin{align*}
  \rho_{\text{tot},\bigtriangleup} %&= \left[ \int_0^\infty d\ln f\, \f{|{2\tilde{H}_\bigtriangleup(f)\sqrt{f}}|^2}{S_n(f)}\right]^{1/2} 
  &=\f{6}{5}A\, h_0 \left[\int_0^{f_\text{ISCO}} d f\, \f{f^{-7/3}}{S_n(f)}\right]^{1/2} \\
  \end{align*}
  \end{footnotesize}
  \\
  %where \begin{small}$\tilde{H}_\bigtriangleup(f)\equiv A\,  \langle |Q|^2_\bigtriangleup\rangle\, h_0 f^{-7/6}= \f{3}{5} A h_0 f^{-7/6}$ \end{small}\\
  \vspace{-5mm}
  Compare with three-L network's \begin{small}$\rho_\text{tot} \approx \tfrac{4}{5}A\, h_0 \left[ \int df \ldots \right]^{1/2} $ \end{small}
  \vspace{10mm}
  %
  %
  \begin{tikzpicture}[overlay,remember picture]
  \node[draw, red,thick,minimum width=5.5cm,minimum height=1.25cm] (b) at (-3.2,1.05){};
  \end{tikzpicture}
  %
  % 
\end{frame}

\begin{frame}{Case study: GW170817}
  \begin{itemize}
    \item 17 August 2017, signal swept from $f\approx \red{30}\,$Hz to $\bl{2000}\,$Hz 
    \onslide<2->\item The event lasted $\approx \red{57}\,$seconds, $\approx \bl{3000}$ GW cycles, $\rho_\text{tot} = \red{32.4}$
    \onslide<3->\item Followed by \red{GRB}170817A 1.7 seconds later
    \onslide<4->\item Rapid localization using L1-H1-V1 $\sim \bl{30}\,\text{deg}^2$
    \onslide<5->\item \red{Optical} counterpart in NGC 4993 11 hours later
  \end{itemize}

  \begin{columns}
  \begin{column}{0.5\textwidth}  %%<--- here
      \begin{center}
      \onslide<3->\includegraphics[height=4cm]{figs/GW_GRB170817.jpg}
      \end{center}
  \end{column}
  \begin{column}{0.5\textwidth}
  %
  \onslide<6->
  {
    Assuming low spin priors
    \begin{align*}
     M&=2.73^{+0.04}_{-0.01} M_\odot \\
     M_c &=1.186^{+0.001}_{-0.001}M_\odot  \\ 
     D&=40.7^{+2.36}_{-2.36}\text{Mpc}
    \end{align*}
  }
  \onslide<7->
  {
    \red{Note:} $M_c$ has the best precision: 
   \begin{small}$${\dot{f}} = \f{96}{5}\pi^{8/3} \left(\tfrac{G M_c}{c^3}\right)^{5/3}\, {f^{11/3}}$$ \end{small}
  }

    \end{column}
  \end{columns}

@@

\begin{frame}{Case study: GW170817}  {Let's put our knowledge to the \red{test}}
\vspace{-7mm}
  \begin{footnotesize}
    \begin{align*}
      &\tau_\text{insp}^{0\text{PN}} \ \ \simeq 55.91\,\text{seconds}, \quad \mathcal{N}_\text{cyc}^{0\text{PN}} \ \ \simeq 2680 \hspace{2cm} (M=2.74 M_\odot) \\
      &\tau_\text{insp}^{3.5\text{PN}} \simeq 56.65\,\text{seconds}, \quad \mathcal{N}_\text{cyc}^{3.5\text{PN}} \simeq 2711 \hspace{2cm} (f_\text{ISCO}\simeq 1605\,\text{Hz}) 
    \end{align*}
  \end{footnotesize}
  \onslide<2->
  {
  What about the SNR? \quad
  \begin{small}$\rho_{\text{tot},\llcorner}  = {\bar\rho_c(f_0)\left[\tilde{A}_h^2 + \tilde{A}_m^2 + \tilde{A}_l^2 \right]^{1/2}}$   
  \end{small}
  }
  %

%
\begin{tikzpicture}[overlay,remember picture]
    \onslide<2->\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(-2cm,-2.cm)}]current page.center) {\includegraphics[height=5cm]{../Figures/GW170817_strains.pdf}};
    \onslide<2->\node (t1 )[anchor=center,scale=1,opacity=1] at ([shift={(3.65cm,0.8cm)}]current page.center) 
    {\begin{footnotesize} 
      $   \bar\rho_c(\red{f_0}) \equiv 2 h_0 \left[ \int_{\red{f_0}}^{{f_\text{ISCO}}} df \f{f^{-7/3}}{S_n(f)}  \right]^{1/2} $      
    \end{footnotesize}}; 
    \onslide<2->\node (t2 )[anchor=center,scale=1,opacity=1] at ([shift={(4.1cm,0.1cm)}]current page.center) 
    {\begin{footnotesize} 
      $ \tilde{A}_{i=h,m,l}=A\left\{\tfrac{4}{5},  \tfrac{2}{5},   < \tfrac{1}{5}\right\}$    
    \end{footnotesize}};  
    \onslide<3->\node (t3 )[anchor=center,scale=1,opacity=1] at ([shift={(4cm,-1.2cm)}]current page.center) 
    {\begin{footnotesize} 
      $\bar\rho_{i} = \left\{29.2, \ 14.6, \ 6.11 \right\}$    
    \end{footnotesize}}; 
    \onslide<4->\node (t4 )[anchor=center,scale=1,opacity=1] at ([shift={(4cm,-2.6cm)}]current page.center) 
    {\begin{footnotesize} 
      $\bar\rho_\text{LHV} = \{ 26.4, 18.8 , 2.0\} $    
    \end{footnotesize}};
    \onslide<3->\node (t4 )[anchor=center,scale=1,opacity=1] at ([shift={(4cm,-1.7cm)}]current page.center) 
    {\begin{footnotesize} 
      $\rho_\text{tot} = 32.6 $    
    \end{footnotesize}};
    \onslide<3->\node[draw, red,thick,minimum width=3.8cm,minimum height=1.1cm] (b) at (10.1,-2.15){};
  \end{tikzpicture}
\end{frame}

\begin{frame}{GW Astronomy in the 2020s}{Advanced LIGO-Virgo}
  \red{BIG question:} how long before the GRB can we {\bf detect} BNS inspirals?\\
  Detection criterion: SNR = \red{15}\\
  Three identical L-IFOs with $Q_{i=h,m,l}$
  %\[  \bar\rho_\text{tot}= \sqrt{\left[\rho_h(f_0^h,\bar{f})\right]^2+\left[\rho_m(f_0^m,\bar{f})\right]^2+\left[\rho_l(f_0^l,\bar{f})\right]^2}=15\]
  % 
  \begin{tikzpicture}[overlay,remember picture]
      \onslide<1->\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(0cm,-1.7cm)}]current page.center) {\includegraphics[height=5.5cm]{../Figures/ALigo_strains.pdf}};
      %\onslide<2->\node (t1 )[anchor=center,scale=1,opacity=1] at ([shift={(3.65cm,0.8cm)}]current page.center) 
      %{\begin{footnotesize} 
      %  $   \bar\rho_c(\red{f_0}) \equiv 2 h_0 \left[ \int_{\red{f_0}}^{{f_\text{ISCO}}} df \f{f^{-7/3}}{S_n(f)}  \right]^{1/2} $      
      %\end{footnotesize}}; 
      %\onslide<3->\node[draw, red,thick,minimum width=3.8cm,minimum height=1.1cm] (b) at (10.1,-2.15){};
  \end{tikzpicture}
